How topos theory can help algebra and geometry

### 2018-07-10 slides-leipzig2018.tex
typo

    \item The approximative version of the intermediate value theorem (stating
    that for any~$\varepsilon > 0$, there is a number~$x$ such that~$|f(x)| <
    \varepsilon$)
    \fixedhref{https://mathoverflow.net/questions/253059/approximate-intermediate-value-theorem-in-pure-constructive-mathematics}{has
    a constructive proof} and therefore holds in~$\Sh(X)$. The
    external interpretation is that in continuous families of continuous
    functions, approximate zeros can locally be picked continuously.

    \item The monotone intermediate value theorem, stating that a strictly
    increasing continuous function with opposite signs has a unique zero,
    admits a constructive proof and therefore holds in~$\Sh(X)$. The external
    interpretation is that in continuous families of strictly increasing
    continuous functions, zeros can globally be picked continuously. You are
    invited to prove this fact directly, without reference to the internal
    language. This exercise isn't particularly hard, but it's not trivial either.
  \end{enumerate}}
\end{frame}

>>>>

    \item The \emph{approximate} intermediate value theorem (stating
    that for any~$\varepsilon > 0$, there is a number~$x$ such that~$|f(x)| <
    \varepsilon$)
    \fixedhref{https://mathoverflow.net/questions/253059/approximate-intermediate-value-theorem-in-pure-constructive-mathematics}{has
    a constructive proof} and therefore holds in~$\Sh(X)$. The
    external interpretation is that in continuous families of continuous
    functions, approximate zeros can locally be picked continuously.

    \item The \emph{monotone} intermediate value theorem, stating that a strictly
    increasing continuous function with opposite signs has a unique zero,
    admits a constructive proof and therefore holds in~$\Sh(X)$. The external
    interpretation is that in continuous families of strictly increasing
    continuous functions, zeros can globally be picked continuously. You are
    invited to prove this fact directly, without reference to the internal
    language. This exercise isn't particularly hard, but it's not trivial either.
  \end{enumerate}}
\end{frame}
